\section{Future Work}
\label{sec:future}
As stated previously, our tests revealed a few short-comings of our system.  Our small scale configuration could not handle the large test sets that we were runing on it, we elected to focus on the server side of our system while ignoring the client side, and the OCR packages were not able to decipher actual receipts with sufficient reliability.

With a primary goal of scallability, we really wanted to see large test sets run through our system with ease.  Unfortunately, we were somewhat limited by the ammount of hardware we could procure over the duration of this project.  Configuring and managing the MySql Cluster nodes requires priledges that were not available to us on department hardware so we were limited to what few computers we could procure.  The results from our tests revealed the bottle-necks to be hardware related, we didn't have enough of it.  Accordingly, we were not satisfied that we suffiently tested the limits of the actual system.  Fortunately we designed our system to scall easily so that if hardware did become available we could incorporate it into the system with ease.  This would likely be the next step in the project so that we can evaluate the limitations of the system on a large scale.

Another goal of our project was to integrate seamlessly with existing POS systems.  Without access to an existing POS configuration nor the means to procure one during the short timeframe for this project, we used an oracle to create simulated receipts.  This issue would have to be resolved before a real-world installation could occur.  We would like to develop a resident client that can be installed on a POS server and interface with the POS system which actually performs the financial transactions.  This would eliminate the need for OCR since the POS system would already have the receipt in a digital form.  It is not clear to us at this point how difficult this portion of the system would be to develop.

While a resident client on the POS server would eliminate the need for OCR for future transactions, it does not allow for customers to store old receipts on our system.  It would be any easy solution to create a web form where end-users could type the information in by hand, but this would be a tedious task.  As a more elegant solution, we would like to develop our own OCR program customized for receipts.  It is unrealistic to expect a general purpose OCR package to be able to decipher all printed text.  In our tests, it was not accurate enough to satisfy our requirements.  However, we believe that a custom OCR package that is developed specifically for receipts would be more successful.  Most receipts have a similar structure which would be an advantage for a custom OCR program.  Additionally, there are not a lot of POS systems in use so there are not a lot of different character sets to accomodate.  A reliable OCR program would be a great benefeit for our system.
